A neural coarse graining theory of consciousness

### 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX

%% Language and font encodings
\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

% Funcitonal content
	% Quotes: green
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

@@

		% callout idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}

@@

		% comment
			% comment by authers
			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}

@@

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes. We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious. This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework. Finally, using the deep learning network, we can measure informational closure in deep hidden layers. Our preliminary results show that informational closure representation emerged after learning. We further decoded the information from the representation and compared it with human conscious perception.
	\end{abstract}

>>>>

%% Language and font encoding
\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

% Functional content
	% Quotes: green
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

@@

		% call-out idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}

@@

		% comment
			% comment by authors
			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}

@@

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes. We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious. This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework. Finally, using the deep learning network, we can measure informational closure in deep hidden layers. Our preliminary results show that informational closure representation emerged after learning. We further decoded the information from the representation and compared it with human conscious perception.
	\end{abstract}
